\mytitle

### 2021-12-07 paper.tex
adding identities

As an application we consider the implementation of the real
dilogarithm, which appears in many physics applications, for example
in the calculation of quantum corrections in quantum electrodynamics.
The real dilogarithm is defined as
%
\begin{align}
  \Li(x) &= -\int_0^x \frac{\log(1-t)}{t}dt, &
  &(x<1).
\end{align}
%
For $|x|<1$ the real dilogarithm has the series representation
%
\begin{align}
  \Li(x) = \sum_{k=1}^\infty \frac{x^k}{k^2}.
  \label{eq:series}
\end{align}
%
Further series representations exist, for example the accelerated
series
%
\begin{align}
  \Li(x) = \sum_{k=0}^\infty \frac{B_k}{(k+1)!} [-\log(1-x)]^{k+1},
\end{align}
%
where $B_k$ are the Bernoulli numbers.  A series representation in
terms of Chebyshev polynomials of the first kind $T_n(x)$ is given in
\cite{luke},
%
\begin{align}
  \Li(x) = \sum_{k=0}^\infty a_n T_n(2x-1),
  \label{eq:cheby}
\end{align}
%
which is used for example in the ROOT program library \cite{root}.
The r.h.s.\ of Eqs.~\eqref{eq:series}--\eqref{eq:cheby} can be summed,
for example, using Horner's scheme or Clenshaw's algorithm
\cite{clenshaw}.  These summation techniques are, however, purely
sequential and thus do not make use of ILP.  In the following an
approximation of the real dilogarithm is presented, which makes use of
ILP, using a rational function approximation in combination with
Estrin's scheme, similarly to the approach use in
Eq.~\eqref{eq:mixed}.

We will define the real dilogarithm $\Li(x)$ for all $x\in\mathbb{R}$
as the real part of the complex continuation $\Li(z)$,
$z\in\mathbb{C}$.  The function can be mapped onto the interval
$[0,1/2)$ by using the following identities:

>>>>

As an application we consider the implementation of the real
dilogarithm, which appears in many physics applications, for example
in the calculation of quantum corrections in quantum field theory.
The real dilogarithm is defined as
%
\begin{align}
  \Li(x) &= -\int_0^x \frac{\log(1-t)}{t}dt, &
  &(x<1).
\end{align}
%
For $|x|<1$ the real dilogarithm has the series representation
%
\begin{align}
  \Li(x) = \sum_{k=1}^\infty \frac{x^k}{k^2}.
  \label{eq:series}
\end{align}
%
Further series representations exist, for example the accelerated
series
%
\begin{align}
  \Li(x) = \sum_{k=0}^\infty \frac{B_k}{(k+1)!} [-\log(1-x)]^{k+1},
\end{align}
%
where $B_k$ are the Bernoulli numbers.  A series representation in
terms of Chebyshev polynomials of the first kind $T_n(x)$ is given in
\cite{luke},
%
\begin{align}
  \Li(x) = \sum_{k=0}^\infty a_n T_n(2x-1),
  \label{eq:cheby}
\end{align}
%
which is used for example in the ROOT program library \cite{root}.
The r.h.s.\ of Eqs.~\eqref{eq:series}--\eqref{eq:cheby} can be summed,
for example, using Horner's scheme or Clenshaw's algorithm
\cite{clenshaw}.  These summation techniques are, however, purely
sequential and thus do not make use of ILP.  In the following an
approximation of the real dilogarithm is presented, which makes use of
ILP, using a rational function approximation in combination with
Estrin's scheme, similarly to the approach use in
Eq.~\eqref{eq:mixed}.

We will define the real dilogarithm $\Li(x)$ for all $x\in\mathbb{R}$
as the real part of the complex continuation of the dilogarithm.  The
real dilogarithm can be mapped onto the interval $[0,1/2)$ by using
the following identities:
%
\begin{align}
  \Li(x) &= -\Li\left(\frac{1}{1-x}\right) - \frac{\pi^2}{6} + \log(1-x)\left[\frac{1}{2}\log(1-x) - \log(-x)\right], \quad (x<-1), \\
  \Li(x) &= -\Li\left(\frac{x}{x-1}\right) - \frac{1}{2}\log^2(x), \quad (-1<x<0), \\
  \Li(x) &= -\Li(1-x) + \frac{\pi^2}{6} - \log(x) \log(1-x), \quad (\frac{1}{2}\leq x<1), \\
  \Li(x) &= \Li\left(1-\frac{1}{x}\right) + \frac{\pi^2}{6} - \log(x)\left[\log\left(1-\frac{1}{x}\right) + \frac{1}{2}\log(x)\right], \quad (1<x<2), \\
  \Li(x) &= -\Li\left(\frac{1}{x}\right) + \frac{\pi^2}{3} - \frac{1}{2} \log^2(x), \quad (x\geq 2).
\end{align}
